О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-18 pps-linear-bound/pps-linear-lower-bound.tex
Missing article 'a'

The solution of Problem~\ref{prb:minimal_shape} (if ever found) will lead to sophisticated packing problem,
something like ``How to put $n$ points in a convex hull of concentric circle and Reuleaux triangle?''
Obviously, Problem~\ref{prb:minimal_shape} can be generalized to higher dimensions.

>>>>

The solution of Problem~\ref{prb:minimal_shape} (if ever found) will lead to a sophisticated packing problem,
something like ``How to put $n$ points in a convex hull of concentric circle and Reuleaux triangle?''
Obviously, Problem~\ref{prb:minimal_shape} can be generalized to higher dimensions.
